Improving Haskell Theory Exploration

### 2015-12-09 TransferReport/related.tex
Fixed rendering issue

However, the way we \emph{use} our clusters to inform theory exploration is similar to that of ACL2(ml). In ACL2(ml), the clusters are used to reason by analogy: finding theorem statements which are similar to the current goal being proved. Once a similar theorem is found, the lemma statements used in its proof are mutated, which includes substituting symbols for those which appear in the same cluster. For example, if we are trying to prove a theorem \texttt{multiply_commutes}, we might find it appears in the same cluster as \texttt{plus_commutes} which was proved using the lemma \texttt{plus_identity} relating \texttt{plus} and \texttt{0}. In this case ACL2(ml) might try mutating \texttt{plus_identity}, for example replacing \texttt{plus} by \texttt{multiply} and \textt{0} by \texttt{1} (assuming those appear in the same clusters); the resulting lemma (which we might call \texttt{multiply_identity}) would be given to ACL2 to try and prove \textt{multiply_commutes}.

>>>>

However, the way we \emph{use} our clusters to inform theory exploration is similar to that of ACL2(ml). In ACL2(ml), the clusters are used to reason by analogy: finding theorem statements which are similar to the current goal being proved. Once a similar theorem is found, the lemma statements used in its proof are mutated, which includes substituting symbols for those which appear in the same cluster. For example, if we are trying to prove a theorem \texttt{multiply\_commutes}, we might find it appears in the same cluster as \texttt{plus\_commutes} which was proved using the lemma \texttt{plus\_identity} relating \texttt{plus} and \texttt{0}. In this case ACL2(ml) might try mutating \texttt{plus\_identity}, for example replacing \texttt{plus} by \texttt{multiply} and \texttt{0} by \texttt{1} (assuming those appear in the same clusters); the resulting lemma (which we might call \texttt{multiply\_identity}) would be given to ACL2 to try and prove \texttt{multiply\_commutes}.
